---
title: "Flight Data Communication Logs Analysis"
author: 
  Group Name:<br>
  late.coders<br>
  <br>
  Team Members:<br>
  Faizal Samiron - WQD180018<br>
  Zulkanain Hasan - WQD180031<br>
date: 18 December 2018
output: slidy_presentation
footer: "Copyright (c) 2018, University of Malaya"
css: "complex-css.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

#Objectives & Case Study

##Objectives
- To **explore** web application for interactive data science presentation (shiny apps & slidy persentation).
- To share our **data visualization** through interactive application.

##Case Study
- **Data communication logs** for reported missing flight Malaysia Airlines **MH370** between 7th March 2014 to 8th March 2014. Data collected from [Malaysia MH370 website]("http://www.mh370.gov.my/en/media2/transcript/category/8-data-communication-logs-for-mh370").
- **Reproduce** the analysis result from UK Air Accidents Investigation Branch (AAIB) report [Link]("http://www.inmarsat.com/news/malaysian-government-publishes-mh370-details-uk-aaib/").
- Signal Communication flow
 **Ground > Satellite > Flight > Satellite > Ground**


#Data Pre-processing
```{r dataset_view, echo = FALSE, message=FALSE, warning=FALSE, results='asis'}
library(DT)
library(dplyr)

dataset <- tbl_df(read.csv("MH370-Data-Log.csv"))

# quick patch row selection. dplyr::filter got issue
dataset <- dataset[dataset$Type == "data", ]

# select required columns
dataset <- dataset %>% 
  select(Time, Channel.Unit.ID, Channel.Type, 
         Burst.Frequency.Offset..Hz..BFO, 
         Burst.Timing.Offset..microseconds..BTO) 

# simplify column names better typing
rename_col <- c("time", "channel_id", "channel_type", "BFO", "BTO")
names(dataset)[1:5] <- rename_col

# convert column channel_id from double to integer
dataset$channel_id <- as.integer(dataset$channel_id)

# refactor column channel_type
dataset$channel_type <-  factor(dataset$channel_type, 
                                levels = c("C-Channel RX", "P-Channel TX", "R-Channel RX", "T-Channel RX"),
                                labels = c("C-RX", "P-TX", "R-RX", "T-RX"))

# replace NA with 0
dataset$BTO[is.na(dataset$BTO)] <- 0
dataset$BFO[is.na(dataset$BFO)] <- 0

# convert datetime to POSIXct
dataset$time <- as.POSIXct(strptime(as.character(dataset$time), 
                                    "%d/%m/%Y %H:%M:%OS"))

DT::datatable(dataset, options = list(pageLength = 3, autoWidth = TRUE), class = 'cell-border stripe')
```

- We are using R in RStudio for data pre-processing
- **filter** rows consist of *Data* observations and **select** target attributes
- convert attributes to appropriate data type format and refactor *channel-type* attribute


#Shiny Apps

- We are using shiny in Rmarkdown for this application.

- We published our Shiny Apps in shinyapps.io at the following [Link]("https://faizalsa.shinyapps.io/shinyApps/").


#Conclusion

- We are able **to utilise** the web applications for interactive application. 
- We are able **to visualize** our data using data communication logs from the missing flight.
- One of the shortcome of current communication system through ping signal transmission is **unable to locate** the exact vessel location.
- In our case study, we can use Shiny Apps to understand the **pattern** on how the system communicate between ground station and vessel before its gone missing.




**THANK YOU**

